**Density Dependence**

### 2022-12-16 Rmd/runDD.Rmd
tidy up

This document provides an example of how to model density dependence in mass-at-age and M-at-age.

@@

The Lorenzen relationship between mass-at-age and M is used to link M and weight-at-age. For example, lorenzen M = a*300^-0.288, so if you want M=0.2 at 300g then a= 0.2 /(300^-0.288)

@@

# Mackerel

>>>>

This document provides an example of how to model density dependence in mass and M-at-age.

@@

The Lorenzen relationship between mass-at-age and M can model M as a function of weight-at-age. For example, lorenzen M = a*300^-0.288, so if you want M=0.2 at 300g then a= 0.2 /(300^-0.288)

@@

# Sumulations
